
In our main specification, foreign forecasters make, on average, forecasting errors that are 6\% larger. We have already shown that the foreign penalty is lower—though not significantly so—for financial and multinational forecasters. We now further examine how the foreign penalty varies with the forecast variable, the forecast horizon, country characteristics, and whether it is state-dependent. To do so, we estimate a regression similar to equation \eqref{eq:geography}:
%In our main specification, foreign forecasters make a 6\% higher error on average. We have already shown that the foreign penalty is lower for financial and multinational forecasters, although not significantly so. We now explore further the extent to which the Foreign penalty varies across the forecast variable, the horizon, country characteristics, and whether it is state-dependent. We do so by estimating a regression that is similar to \eqref{eq:geography}:

\begin{align}
	\ln(|Error_{ijt,t+h}^{m,x}|)= \delta_{it,h}^{m,x} +\tilde\delta_{jt,h}^{m,x} +  \beta \text{Foreign}_{ij} +\gamma \text{Foreign}_{ij}\times X_{ijt,h}^{m,x}+ \varepsilon_{ij,t}^m  \,, \label{eq:heterogeneity}
\end{align}
Here, $X_{ijt,h}^{m,x}$ is a set of variables that varies either across the forecast variable (growth and inflation), horizon (current or future), time, country, or time and country, so that the levels are already absorbed by the fixed effects. If the $\gamma$ coefficients are significant, it means that the foreign penalty is heterogeneous across that dimension. It will be useful though to also examine how the linear term $X_{ijt,h}^{m,x}$ affects the errors to answer the question: is the foreign penalty larger in situations where the errors are also larger? To identify the role of $X_{ijt,h}^{m,x}$, we will need to remove some fixed effects. In these specifications, we keep our \textit{Foreign} dummy as a control, but we do not interpret its estimated effect, since we will be neglecting some of the potential confounding factors and noise that we are controlling for in our main specification with richer fixed effects.

We begin by examining the role of the forecast variable and the forecast horizon. Specifically, we define \textit{GDP} as a dummy variable equal to 1 if the forecast targets GDP growth, and 0 if it targets inflation. \textit{Future} is a dummy equal to 1 if the forecast refers to the next calendar year, and 0 if it refers to the current year. Finally, \textit{Month-of-year} is a categorical variable ranging from 1 to 12, indicating the month in which the forecast is made.


The results are presented in Table \ref{tab:error_reg_labs_cs}. Column (1) examines how forecast errors vary with \textit{GDP}, \textit{Future}, and \textit{Month-of-year}. This specification includes only country-year and forecaster-year fixed effects to preserve sufficient variation in the explanatory variables. The estimates show that forecast errors are larger for GDP growth forecasts and for forecasts targeting the future year. Notably, forecast errors decline over the course of the year, which suggests that information flows continuously during the year. Column (5) explores how the foreign penalty interacts with these variables. It includes forecaster-date-variable-horizon and country-date-variable-horizon fixed effects, which absorb the main effects of \textit{GDP}, \textit{Future}, and \textit{Month-of-year}. The results indicate that the foreign penalty is significantly lower for GDP growth and for forecasts of the future year. Interestingly, the penalty increases over time within the year. As shown in Panel (a) of Figure \ref{fig:heterogeneity} in the Appendix, the average foreign penalty rises across calendar months. This pattern suggests that, somewhat paradoxically, the foreign penalty is larger when overall forecast uncertainty is lower.



%The results are reported in Table \ref{tab:error_reg_labs_cs}. Column (1) shows how the forecast error depends on $GDP$, $Future$ and $Month-of-year$. This regression includes only country-year and forecaster-year fixed effects to avoid absorbing all the variation in the explanatory variables. It shows that forecast errors are higher for GDP growth and for the future year. Noticeably, the forecast errors diminish over time within a given year, which suggests that information flows continuously during the year. 


%Column (5) shows the impact of the interaction of Foreign with these variables. It includes forecaster-date-variable-horizon and country-date-variable-horizon fixed effects, so the linear impact of $GDP$, $Future$ and $Month-of-year$ are fully absorbed with this fixed-effect specification. It shows that the foreign penalty is significantly lower for GDP growth and for the future year. Interestingly, the penalty increases over time within a given year.\footnote{Panel (a) of Figure \ref{fig:heterogeneity} in the Appendix shows the average foreign penalty per month, which appear to be increasing over the course of the year.}  This evidence shows that, somehow paradoxically, the foreign penalty is higher when there is less forecasting uncertainty.

As shown in Column (6), the foreign penalty does not exhibit state dependence: it does not increase significantly during recessions or periods of global uncertainty, measured by the \textit{VIX}, while Column (2) shows that forecast errors are on average larger during periods of heightened uncertainty and in recessions. This suggests that while both local and foreign forecasters make larger errors in adverse times, the relative difference between them remains stable.

We also consider several country-specific characteristics: an \textit{Emerging} economy dummy, institutional quality (from the World Development Indicators, in the table referred to as \textit{Institutions}), and country size (\textit{log of GDP }evaluated at purchasing power parity).\footnote{The data sources are the following: country size \citep{cpigravity22} and quality of institutions \citep{wdi22}. The list of emerging economies is given in the Appendix Table \ref{tab:app_emerging_advanced}.}



In Column (7), the foreign penalty does not differ between emerging and advanced economies, nor does it depend on institutional quality, while Column (3) shows that, on average, errors are larger for emerging economies, and that stronger institutions are associated with a lower error. However, the foreign penalty is higher for larger countries, for which errors are lower on average (Column (4)). As with the forecast variable and horizon, lower average uncertainty is linked to a higher foreign penalty. The main picture is unchanged when putting together all the interaction terms (Column (8)).\footnote{In the Appendix Table \ref{tab:error_reg_labs_cs_ind}, we show that the results do not change either when we interact the Foreign dummy with one variable at a time. Additionally, Figure \ref{fig:heterogeneity} in the Appendix displays the Foreign coefficients per year, month and country. Panel (a) shows the average foreign penalty per month, which appear to be increasing over the course of the year. Panel (b) shows the average foreign penalty per year. No systematic pattern appears, which is consistent with our results. Panel (c) shows the average country penalty per country. The estimates are heterogeneous across countries but no systematic difference between Emerging and Advanced economies appears, confirming our results. We also conduct a similar analysis, using the estimated coefficients from our asymmetric information tests, $\beta^{FE}$ and $\beta^{DIS}$. The results, which are shown in Table \ref{tab:FE_reg_mg}, are broadly consistent with the evidence on the errors, except that they are less precisely estimated.}

%\footnote{Information frictions are more prevalent in the later months of the year ($\beta^{FE}$ is less negative), and the foreign penalty is stronger for these months (the interaction between the month variable and the Foreign dummy has a negative effect on $\beta^{FE}$ and $\beta^{DIS}$ depends negatively on the month variable). Similarly, forecasters forecast larger countries better on average ($\beta^{FE}$ is less negative), but foreign forecasters typically have a larger disadvantage when forecasting larger countries ($\beta^{DIS}$ is significantly more negative for larger countries).}

{\setstretch{1}
	\input{../output/tables/error_reg_labs_cs}
}

\paragraph{Discussion}


The asymmetry of information between local and foreign forecasters is unaffected by the development status of the economy or the quality of institutions. This aligns with existing evidence: \citet{Baeetal2008}, who study whether local analysts are better at forecasting local firms' earnings, find that investor protection and the country's development status do not influence the foreign penalty.


%The asymmetry of information between local and foreign forecasters is not affected by the development status of the economy that is being forecasted, or by the quality of institutions. This is not surprising with regards to existing evidence. Indeed, \citet{Baeetal2008}, who examine whether local analysts are better at forecasting local firms' earnings, find that the protection of investors' rights does not influence the foreign penalty, nor does the development status of the country where the firms are located.%\footnote{In their paper, \citet{Baeetal2008} show that variables that improve the functioning of the local stock market lower the local advantage (for instance, business disclosure). However, we show that these variables are not relevant when it comes to forecast aggregate outcomes.}

We do find that variables such as country size, the forecast variable, and the forecast horizon influence the foreign penalty. However, the penalty is generally higher when forecasting uncertainty is lower, suggesting that local forecasters are better at finding and exploiting available macroeconomic information. These results are consistent with the locals' better access to locally-produced information (by knowing when and where relevant information is released). The stronger information asymmetry for current-year GDP growth or inflation forecasts, and its increase over the year (greater in December than January), is consistent with the assumption that local forecasters are exposed to the regular releases of partial GDP growth and inflation figures and integrate this information faster. Interestingly, inflation is typically available at a higher frequency and with a shorter lag than GDP, making the access to that information an even greater advantage. This is consistent with Table \ref{tab:updating_errors_main_small}, where we can see that the difference in updating frequency is 2\% larger for inflation forecasts than for GDP growth forecasts.
